---
title: "Project 2"
author: "Kristen Akey, kka2120"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(lubridate)
library(viridis)
library(sf)
```


```{r}
chi <- read_csv("raw-data/crime_data/Chicago/chicago_crimes_2018.csv")
```


```{r}
## create date/time variables

# date ony variable
chi$Date_simp <- substr(chi$Date, 1, 10)
a<-as.factor(chi$Date_simp)
abis<-strptime(a,format="%m/%d/%Y", tz="UTC") #defining what is the original format of your date
chi$Date_simp<-as.Date(abis,format="%Y-%m-%d")

# time variable
chi$time <- format(strptime(trimws(substr(chi$Date, 11, 22), which="both"), "%I:%M:%S %p"), "%H:%M:%S")
```


```{r}
# 'night' crimes
```




# summary descriptive statistics

```{r}
# top overall crimes
top_crimes <- chi %>%
  select(Date, `Primary Type`) %>%
  count(`Primary Type`) %>%
  arrange(desc(n)) 
top_crimes
```

```{r}
# top "night" crimes
top_night_crimes <- chi %>%
  select(Date_simp, time, `Primary Type`) %>%
  filter(time >="22:00:00" | time <= "06:00:00") %>%
  count(`Primary Type`) %>%
  arrange(desc(n)) 
top_night_crimes
```




```{r}
top_five<- top_crimes %>%
  head(5) %>% pull(`Primary Type`)

chi %>%
  select(Date_simp, `Primary Type`) %>%
  filter(`Primary Type` %in% c(top_five, "NARCOTICS")) %>%
  arrange(Date_simp) %>%
  group_by(Date_simp) %>%
  count(`Primary Type`) %>%
  ggplot(., aes(Date_simp, n, color=`Primary Type`)) +
  geom_line()
```

******************************************************************

### Theft Crime counts overtime, 2018

```{r}
# date variables for geom_tile plot
chi$month <- month(as.POSIXlt(chi$Date_simp, format="%Y/%m/%d"))
chi$year <- year(as.POSIXlt(chi$Date_simp, format="%Y/%m/%d"))
chi <- chi %>%
  mutate(month_year = paste0(as.character(month),"-",as.character(year)))
chi$weekday <- wday(
  chi$Date_simp,
  label = T,
  abbr = TRUE,
  week_start = getOption("lubridate.week.start", 1)
)
chi$weeknum <- week(chi$Date_simp)
chi$daynum <-day(chi$Date_simp)
```

```{r}
chi %>%
  # select(Date_simp, `Primary Type`) %>%
  filter(`Primary Type`=="THEFT") %>%
  arrange(Date_simp) %>%
  group_by(Date_simp) %>%
  mutate(n = n()) %>%
  ggplot(., aes(x = weeknum, y = weekday, fill = n)) +
  geom_tile(col = "black", width = .95, height = .9) +
  # facet_wrap(vars(year), strip.position = "top", nrow = 3) +
  scale_fill_viridis(option="inferno", #end = .9, labels = function(x) paste0(x, "%"),
                     name="", direction = -1) +
  scale_x_continuous(expand = c(0, 0),
                    breaks = seq(1, 52, length = 12),
                    labels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun",
                               "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))  +
  xlab("") + ylab("") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        text = element_text(family="Lato"),
        legend.justification = c(.95, 0),
        legend.position = "bottom",
        legend.margin = margin(-0.25,-0.5,0,-0.5, unit="cm"),
        plot.margin =  margin(.5,.5,.5,.5, unit="cm"),
        legend.key.width = unit(.8, "cm"),
        plot.title = element_text(vjust=2.4, size=14),
        plot.subtitle = element_text(size=9, vjust=1),
        plot.caption = element_text(size=7, vjust=-15)
        ) +
  ggtitle("Chicago Theft Crime Counts, 2018")
```


-- time of day? 
-- does the day of week change?
-- weather beginning of 2018? correlation between weather and crime
-- holidays?
-- Spatially?

********************************************************************************


```{r}
beats_shp <- read_sf('raw-data/crime_data/Chicago/Boundaries-Police_Beats_current/geo_export_fb1cc8b1-500e-49cd-a492-47f82d2121a5.shp')
```


```{r}
chi <- chi %>% rename(beat_num = Beat )

tot_arrest_data <- chi %>%
  group_by(beat_num) %>%
  mutate(tot_arrest = sum(Arrest)) %>%
  select(beat_num, tot_arrest) %>%
  distinct()

tot_arrest_shp <- left_join(beats_shp, tot_arrest_data, by="beat_num") #

tot_arrest_shp$tot_arrest_cat <- cut(tot_arrest_shp$tot_arrest, 
                                     breaks = c(0, 250,500,750,1000,1250), 
                              labels = c("250","500","750","1000","1250"))

tot_arrest_shp %>%
  filter(!is.na(tot_arrest_cat)) %>%
ggplot(.) + 
  geom_sf( aes(fill=tot_arrest_cat),size=.3) +
  theme_void() +
  scale_fill_brewer(palette = "RdPu", na.value = "grey80",
                  name="Total Arrests") +
  ggtitle("Chicago Arrests by Police Beat, 2018") +
    theme(panel.grid.major = element_line("transparent"), 
        axis.text = element_blank(),
        text=element_text(family="Noto Serif")) 

sum(tot_arrest_shp$tot_arrest, na.rm=T)
```


```{r}
# all reported crimes by police beat

tot_crime_data <- chi %>%
  group_by(beat_num) %>%
  mutate(tot_crime = n()) %>%
  select(beat_num, tot_crime) %>%
  distinct()

tot_crime_shp <- left_join(beats_shp, tot_crime_data, by="beat_num") #

tot_crime_shp$tot_crime_cat <- cut(tot_crime_shp$tot_crime, 
                                     breaks = c(0, 500,1000,1500,2000,2500,3000,3500), 
                          labels = c("500","1000", "1500","2000","2500", "3000", "3500"))

tot_crime_shp %>%
  filter(!is.na(tot_crime_cat)) %>%
ggplot(.) + 
  geom_sf( aes(fill=tot_crime_cat),size=.3) +
  theme_void() +
  scale_fill_brewer(palette = "YlGnBu", na.value = "grey80",
                  name="Total Crimes") +
  ggtitle("Chicago Crimes Reported by Police Beat, 2018") +
    theme(panel.grid.major = element_line("transparent"), 
        axis.text = element_blank(),
        text=element_text(family="Noto Serif")) 
```

********************************************************************************

Spatially?
Lights?

```{r}
library(tidyverse)
```

```{r}
# https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Street-Lights-All-Out-Histori/zuxi-7xem/data
allout <- read_csv("raw-data/311_Service_Requests_-_Street_Lights_-_All_Out_-_Historical.csv")

allout$creation_date <-as.Date(allout$`Creation Date`,format="%m/%d/%Y")
allout$completion_date <-as.Date(allout$`Completion Date`,format="%m/%d/%Y")

allout$creation_date_year <- format(allout$creation_date, format = "%Y")
allout <- allout %>% filter(creation_date_year==2018)


# https://data.cityofchicago.org/Service-Requests/311-Service-Requests-Street-Lights-One-Out-Histori/3aav-uy2v/data
oneout <- read_csv("raw-data/311_Service_Requests_-_Street_Lights_-_One_Out_-_Historical.csv")

oneout$creation_date <-as.Date(oneout$`Creation Date`,format="%m/%d/%Y")
oneout$completion_date <-as.Date(oneout$`Completion Date`,format="%m/%d/%Y")
oneout$creation_date_year <- format(oneout$creation_date, format = "%Y")
oneout <- oneout %>% filter(creation_date_year==2018)
```

```{r}
lights_out <- allout %>% rbind(.,oneout)
```


What areas had more duplicated requests?
```{r}

```



```{r}
lights_out <- lights_out %>%
  filter(Status=="Completed") %>%
  mutate(time_to_complete_all = completion_date- creation_date) %>%
  group_by(`Type of Service Request`) %>%
  mutate(time_to_complete_status = completion_date- creation_date)

ggplot(lights_out, aes(time_to_complete_all)) + 
  geom_histogram() +
  ggtitle('Distribution of Time to Complete in Days')
```

```{r}
quantile(as.numeric(lights_out$time_to_complete_all))
mean(as.numeric(lights_out$time_to_complete_all))
```


```{r}
ggplot(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",],
       aes(time_to_complete_status)) + 
  geom_histogram() +
  ggtitle('Distribution of Time to Complete in Days - All/Out')
```


```{r}
ggplot(lights_out[lights_out$`Type of Service Request`=="Street Light Out",],
       aes(time_to_complete_status)) + 
  geom_histogram() +
  ggtitle('Distribution of Time to Complete in Days - Street Light Out')
```

```{r}
quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status))
mean(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status))


quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status))
mean(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status))
```


**********************************************************************

Remove outliers
```{r}
#find Q1, Q3, and interquartile range for values in column A
Q1 <- quantile(as.numeric(lights_out$time_to_complete_all), .25)
Q3 <- quantile(as.numeric(lights_out$time_to_complete_all), .75)
IQR <- IQR(as.numeric(lights_out$time_to_complete_all))

#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
no_outliers <- subset(lights_out, as.numeric(lights_out$time_to_complete_all)> (Q1 - 1.5*IQR) & as.numeric(lights_out$time_to_complete_all)< (Q3 + 1.5*IQR))

#view row and column count of new data frame
dim(no_outliers) 

ggplot(data=no_outliers, aes(as.numeric(time_to_complete_all))) +
  geom_histogram() +
  ggtitle("Distribution of Time to Complete in Days - Outliers Removed")
```

```{r}
mean(as.numeric(no_outliers$time_to_complete_all))
```


********************************************

```{r}
#find Q1, Q3, and interquartile range for values in column A
Q1 <- quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status), .25)
Q3 <- quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status), .75)
IQR <- IQR(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status))


#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
no_outliers <- subset(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",], as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status)> (Q1 - 1.5*IQR) & as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status)< (Q3 + 1.5*IQR))

#view row and column count of new data frame
dim(no_outliers) 

ggplot(data=no_outliers, aes(as.numeric(time_to_complete_status))) +
  geom_histogram()
```

```{r}
mean(as.numeric(no_outliers$time_to_complete_all))
```

********************************************

```{r}
#find Q1, Q3, and interquartile range for values in column A
Q1 <- quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status), .25)
Q3 <- quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status), .75)
IQR <- IQR(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status))


#only keep rows in dataframe that have values within 1.5*IQR of Q1 and Q3
no_outliers <- subset(lights_out[lights_out$`Type of Service Request`=="Street Light Out",], as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status)> (Q1 - 1.5*IQR) & as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status)< (Q3 + 1.5*IQR))

#view row and column count of new data frame
dim(no_outliers) 

ggplot(data=no_outliers, aes(as.numeric(time_to_complete_status)))  +
  geom_histogram()
```

```{r}
mean(as.numeric(no_outliers$time_to_complete_all))
```

**************************************************

```{r}
# remove na lat/long
lights_out <- lights_out %>%
  filter(!is.na(Latitude))
# convert dataframe to spaital data
lights_out_sf <- st_as_sf(lights_out, coords = c("Longitude", "Latitude"), crs = st_crs(beats_shp))

beats_lights_shp <- beats_shp %>%
  st_join(lights_out_sf) 

### complete by community area
```















************************************************************************

### BY BEAT NUMBER

#### Occurances

```{r}
beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Lights - All/Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =n(),
         num_out_cat = cut(num_out,
                 breaks = c(0, 50,100,150,200), 
                              labels = c("50","100","150","200")) 
         ) %>%
  ggplot() +
    geom_sf(aes(fill=as.factor(num_out_cat))) +
    theme_void() +
    scale_fill_brewer(
                  na.value = "grey80",
                  name="Number of All\nLights Out Complaints") +
  ggtitle("Number of 311 All Lights Out Complaints by Police Beat, 2018") +
    theme(panel.grid.major = element_line("transparent"), 
        axis.text = element_blank(),
        text=element_text(family="Noto Serif")) 
```


```{r}
beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Light Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =n(),
         # num_out_cat = cut(num_out,
         #         breaks = c(0, 50,100,150,200, 250, 300), 
         #                      labels = c("50","100","150","200", "250", "300")) 
          num_out_cat = cut(num_out,
                 breaks = c(0,100,200,  300), 
                              labels = c("100","200", "300")) 
         ) %>%
  ggplot() +
    geom_sf(aes(fill=as.factor(num_out_cat))) +
    theme_void() +
    scale_fill_brewer(
                  na.value = "grey80",
                  name="Number of Light Out Complaints") +
  ggtitle("Number of 311 Light Out Complaints by Police Beat, 2018") +
    theme(panel.grid.major = element_line("transparent"), 
        axis.text = element_blank(),
        text=element_text(family="Noto Serif")) 
```


#### Time to Complete


```{r}
beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Lights - All/Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =as.numeric(median(time_to_complete_status)),
         num_out_cat = cut(num_out,
                 breaks = c(0, 1,2,4,194),
                              labels = c("25%","50%","75%","100% "))
         ) %>%
  ggplot() +
    geom_sf(aes(fill=as.factor(num_out_cat))) +
    theme_void() +
    scale_fill_brewer(
                  na.value = "grey80",
                  name="Number of All\nLights Out Complaints") +
  ggtitle("Number of 311 All Lights Out Complaints by Police Beat, 2018") +
    theme(panel.grid.major = element_line("transparent"), 
        axis.text = element_blank(),
        text=element_text(family="Noto Serif")) 
```


```{r}
quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status))
mean(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Lights - All/Out",]$time_to_complete_status))
```



```{r}
quantile(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status))
mean(as.numeric(lights_out[lights_out$`Type of Service Request`=="Street Light Out",]$time_to_complete_status))
```





****************************************************************

### What is the relationship betwwen light outages and crime?

```{r}
# join light outage data with crime data
crime_lights <- chi %>%
  group_by(Date_simp) %>%
  mutate(crime_n_by_date = n()) %>%
  select(Date_simp, crime_n_by_date) %>%
  rename("creation_date"="Date_simp") %>%
  distinct(creation_date, .keep_all=T)
  right_join(., lights_out, by = c("Date_simp" = "creation_date"))

lights_out
```



******************************************************************

### Where are the outliers occuring?

Areas with the slowest median responses
```{r}
outlier_beats <- unique(beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Lights - All/Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =as.numeric(median(time_to_complete_status))) %>%
  filter(num_out>4) %>%
  pull(beat_num))

beats_lights_shp %>%
  mutate(indic = ifelse(beat_num %in%outlier_beats,1,0)) %>%
ggplot() +
    geom_sf(aes(fill=as.factor(indic))) +
    theme_void() 
```


Areas with the fastest median responses
```{r}
bestoutlier_beats <- unique(beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Lights - All/Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =as.numeric(median(time_to_complete_status))) %>%
  filter(num_out<=1) %>%
  pull(beat_num))

beats_lights_shp %>%
  mutate(indic = ifelse(beat_num %in%bestoutlier_beats,1,0)) %>%
ggplot() +
    geom_sf(aes(fill=as.factor(indic))) +
    theme_void() 
```


Is this the same for one light out compalints?

Areas with the slowest median responses
```{r}
outlier_beats <- unique(beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Light Out") %>%
  group_by(beat_num) %>%
  mutate(num_out =as.numeric(median(time_to_complete_status))) %>%
  filter(num_out>12) %>%
  pull(beat_num))

beats_lights_shp %>%
  mutate(indic = ifelse(beat_num %in%outlier_beats,1,0)) %>%
ggplot() +
    geom_sf(aes(fill=as.factor(indic))) +
    theme_void() 
```



************************************************************************

Median number of days with all data
```{r}
beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Lights - All/Out") %>%
  group_by(beat_num) %>%
  mutate(time_to_complete =median(as.numeric(time_to_complete_all))) %>%
  ggplot() +
    geom_sf(aes(fill=as.factor(time_to_complete)))
```


```{r}
beats_lights_shp %>%
  filter(`Type of Service Request`=="Street Light Out") %>%
  group_by(beat_num) %>%
  mutate(time_to_complete =median(as.numeric(time_to_complete_all))) %>%
  ggplot() +
    geom_sf(aes(fill=as.factor(time_to_complete)))
```




******************************************************************************
```{r}
beats_shp %>% 
  group_by(`Community Area`) %>% 
  st_cast() 

chi
```







******************************************************************************

```{r}
police_districts <- beats_shp %>% 
  group_by(district) %>% 
  st_cast() 

```


```{r}
police_districts %>%
  left_join(., no_outliers, by)
```

